Initial Analysis

### 2019-10-23 Initial_Analysis.Rmd
Clean script

#### Function 'Mclapply_Hack'

@@

# The hack
# https://www.r-bloggers.com/implementing-mclapply-on-windows-a-primer-on-embarrassingly-parallel-computation-on-multicore-systems-with-r/

@@

## Principal Routine

#### Control Pannel

```{r EEZ_Control_Pannel, eval = T, echo = F}

@@

# Determine forlder for saving results
Folder <- "Trans_Results"
Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")

if(file.exists(Results_Path) == TRUE){
  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
}else{
  dir.create(paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = ""))
  Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",Folder,"/",sep = "")
}

@@

# Just a warning for me not to forget
print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level and will be saved at",Folder))
```

#### Run Routine
```{r Routine_parallel, eval = F, echo = F}

@@

## Function `GetTransResults`

@@

## Function `CleanResults`

```{r cleaning_function, eval = T, echo = F}

@@

# Clean out countries that share with their own borders (e.g. USA gulf of Mx and East coast)
  Auto_Remove_Territories <- Data %>%   
    rename(FishingRegion=Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(TaxonKey,
           Territory= FishingRegion,
           FishingRegion=Neighbour, 
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(1,2, 
           Neighbour = FishingRegion,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

@@

  # List of territories to eliminate (No other neighobors but mainland)

  Islands_to_Remove <- c(
    "Brazil (Fernando de Noronha)",
    "Brazil (St Paul and St. Peter Archipelago)",
    "Hawaii Main Islands (USA)",
    "Hawaii Northwest Islands (USA)",
    "Juan Fernandez Islands (Chile)",
    "Kermadec Isl. (New Zealand)"
  )

  # Complete list of territories to remove from dataset (Including islands)

  Territories_to_Remove <- Data %>% 
    filter(
      Territory %in% Islands_to_Remove |
        Neighbour %in% Islands_to_Remove |
        Territory == "Balearic Island (Spain)" & Neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
        Territory == "British Virgin Isl. (UK)" & Neighbour == "Anguilla" |
        Neighbour == "British Virgin Isl. (UK)" & Territory == "Anguilla" |
        Territory == "Corsica (France)" & Neighbour == "France (Mediterranean)" |
        Neighbour == "Corsica (France)" & Territory == "France (Mediterranean)" |
        Territory == "Crete (Greece)" & Neighbour == "Grece" |
        Neighbour == "Crete (Greece)" & Territory == "Grece" |
        Territory == "Cyprus (North)" & Neighbour == "Cyprus (South)" |
        Neighbour == "Cyprus (North)" & Territory == "Cyprus (South)" |
        Territory == "Channel Isl. (UK)" & Neighbour == "United Kingdom" |
        Neighbour == "Channel Isl. (UK)" & Territory == "United Kingdom" |
        Territory == "Glorieuse Islands (France)" & Neighbour == "Mayotte (France)" |
        Neighbour == "Glorieuse Islands (France)" & Territory == "Mayotte (France)" |
        Territory == "Guam (USA)" & Neighbour == "Northern Marianas (USA)" |
        Neighbour == "Guam (USA)" & Territory == "Northern Marianas (USA)" |
        Territory == "Italy" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Italy" & Territory == "Sardinia (Italy)" |
        Territory == "Italy" & Neighbour == "Sicily (Italy)" |
        Neighbour == "Italy" & Territory == "Sicily (Italy)" |
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (main islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (main islands)"|
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (Ogasawara Islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (Ogasawara Islands)"|
        Territory == "Norway" & Neighbour == "Svalbard Isl. (Norway)" |
        Neighbour == "Norway" & Territory == "Svalbard Isl. (Norway)" |
        Territory == "Sicily (Italy)" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Sicily (Italy)" & Territory == "Sardinia (Italy)" |
        Territory == "South Africa (Atlantic Coast)" & Neighbour == "South Africa (Indian Ocean Coast)" |
        Neighbour == "South Africa (Atlantic Coast)" & Territory == "South Africa (Indian Ocean Coast)" |
        Territory == "USA (Alaska, Arctic)" & Neighbour == "USA (Alaska, Subarctic)" |
        Neighbour == "USA (Alaska, Arctic)" & Territory == "USA (Alaska, Subarctic)"
    ) %>%
    group_by(Territory,Neighbour) %>% 
    summarise(n())

  # Cleaned results 
  Clean_Results <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9) %>% 
    # Fixe coding issues between MAC and Windows
    mutate(
    Territory = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Territory),
    Territory = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Territory),
    Territory = gsub("R<e9>union (France)","Réunion",Territory),
    Neighbour = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Neighbour),
    Neighbour = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Neighbour),
    Neighbour = gsub(" R<e9>union (France)","Réunion",Neighbour)
    )

@@

@@

# Set Jurisdiction to EEZ or RFMO
Jurisdiction <- "EEZ"
Folder <- "Trans_Results"

# Updates result's path for the jurisdiction
Results_Path <- paste(Results_Path,Jurisdiction,"/",Folder,"/",sep="")

@@

# Load Land shapefile
path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")
# #The File
fnam_world_land <- "ne_50m_admin_0_countries.shp"

World_land_sf <- st_read(dsn = path_world_land,
                         layer =file_path_sans_ext(fnam_world_land)) %>% 
  rename(Territory = NAME)

@@

# Load EEZ shapefiles 
# SAU shapefile name and paths

@@

if(Sys.info()[7] == "carmelia"){ # For Carmelia

  Clean_Results_Trans <- read.csv(paste(Data_Path,"Clean_Results.csv",sep="")) # losad carmelia data
}else{  # For Hall and The Beast

@@

  # Read SAu Status Data
  Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep ="")) %>% 
    rename(TaxonKey = Species)

@@

  # Load and clean Transboundary results
  Results_Trans <- GetTransResults(Spp)

@@

} # closes ifstatement for carmelia temporal files

@@

```{r Results_Tresholds, eval =F, echo = F}

#### Determine transboundary stocks and countries based on selected trsholds ####

@@

```{r Data_per_Territory}

@@

@@

Catch_Country <- Sau_Catch_Data %>% 
  group_by(FishingRegion=Territory) %>% 
  summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
  filter(!(is.na(FishingRegion))) %>% 
  left_join(Clean_sau_eez_fes) %>% 
  group_by(Territory = fishing_entity) %>% 
  summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
  mutate(Territory = gsub("USA","United States of America",Territory))

# Or revenue data %>%

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, Territory = fishing_entity) %>% 
  summarise(n=n()) %>% 
  select(-n) %>% 
  left_join(Tresholded_T_Data_x) %>% 
  left_join(Sau_Revenue_Data) %>% 
  group_by(Territory) %>% 
  summarise(Total_USD = (sum(Mean_Value,na.rm=T))/1000000) %>% 
  mutate(Territory = ifelse(Territory == "USA","United States of America",Territory),
         Bins = cut(Total_USD,breaks = 4),
         Bins_Plot = cut(Total_USD,breaks = 4,
                    labels = c('super low', 'low','high','super high'))
         ) %>% 
  filter(Total_USD > 0)

@@

@@

# Data <- World_sf_si_land %>% 
#   as_tibble() %>% 
#   select(Territory, BinsLan)
# 
# Data_EEZ <- World_sf_si %>% 
#   as_tibble() %>% 
#   select(Territory, Bins)
# 
# 
# ### EEZ shapefile
# eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
# 
# eez = spTransform(eez, CRS("+proj=longlat"))
# eez = spTransform(eez, CRS("+proj=wintri"))
# eez = fortify(eez) 
# 
# World_sf_si <- World_sf %>%
#   st_transform(crs = 4326
# 
# #### Round map tryout 
# mapworld = fortify(spTransform(rworldmap::getMap(), CRS("+proj=wintri")))
# 
# mapworld<- mapworld %>% 
#   rename(Territory = id) %>% 
#   left_join(Data,
#             by = "Territory") %>% 
#   left_join(Data_EEZ,
#             by = "Territory") %>% 
#   rename(id = Territory)
# 
# # head(mapworld)
# 
# #create map boundary
# ll.to.wt <- function (points)
#   as.data.frame(spTransform(SpatialPoints(points, CRS("+proj=longlat")),
#                             CRS("+proj=wintri")))
#  
# lseq = seq(-85, 85, by=.25)
# boundary <- ll.to.wt(data.frame(
#   long = c(rep(-180, length(lseq)), rep(180, length(lseq)), -180),
#   lat  = c(lseq,                    rev(lseq),          lseq[1])))
#  
# # New facet label names for dose variable
# ggplot()+
#   geom_polygon(data=boundary, aes(x=long, y=lat), fill="azure") +
#   geom_map(data=mapworld, map=mapworld, aes(map_id=id, x=long, y=lat), fill ="gray93", colour=NA) +
#   geom_polygon(data = mapworld, 
#                aes(
#                  x = long,
#                  y = lat,
#                  group = group,
#                  fill = BinsLan
#                ),
#                colour="grey") +
#   geom_polygon(data = mapworld, 
#                aes(
#                  x = long,
#                  y = lat,
#                  group = group,
#                  fill = Bins)
#                ) +
#   geom_path(data=eez, aes(x=long,y=lat, group=group),colour="grey") +
  # geom_point(data=ui, aes(x=long, y=lat, size=M, color=M), alpha=0.9) +
  # geom_text_repel(data=ui,aes(x=long, y=lat, label=un.name), size=2.5, color = 'black',
  #                 box.padding = unit(0.5, "lines"),
  #                 point.padding = unit(0.5, "lines"),
  #                 segment.color = 'grey50') +
  # scale_radius(range = c(1, 2)) #+
  # scale_colour_distiller(palette ="Spectral", direction = 1, limits=c(0,1), breaks=c(c(0,1))) + # or direction=1
  # theme_map()+
#   theme(legend.key = element_blank(),
#         strip.background = element_blank(),
#         legend.position = "none",
#         text = element_text(size=12,face="bold"))+
#   facet_wrap(~variable, scales = "free", ncol=1)+scale_shape(guide=FALSE)+scale_size(guide=FALSE)
# y=tag_facet(q, tag_pool = c("d","e","f"))

@@

```{r Circular_Data, eval = T, echo = F}

@@

```{r n_species_country, eval = T, echo =F}

@@

# Use rfishbase to get species environment

Species_list <- Species_Trans %>% 
  mutate(scientific_name = paste(Genus,Species)) %>% 
  pull(scientific_name)

Species_environ_list <- rbind(species(Species_list, 
                                      fields = species_fields$habitat[4])
) %>% 
  mutate(scientific_name = Species_list)

Species_Data <- Tresholded_T_Data %>% 
  group_by(TaxonKey) %>% 
  summarise(n_trans_spp = length(unique(Territory))) %>% 
  left_join(Exploited_Species) %>%
  rename(scientific_name = TaxonName) %>% 
  left_join(Species_environ_list) %>%
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag)),
         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp)) %>% 
  select(individual=scientific_name,
         value = n_trans_spp,
         group = DemersPelag) %>% 
  arrange(group,value) %>% 
  filter(value > 20)  # remove all species under 10 (way too many to plot!)

@@

Char <- as.factor(Species_Data$group)

# Set a number of 'empty bar' to add at the end of each group
empty_bar <- 2
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
colnames(to_add) <- colnames(Species_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Species_Data <- rbind(Species_Data, to_add)
Species_Data <- Species_Data %>% arrange(group,value)
Species_Data$id <- seq(1, nrow(Species_Data))

@@

# Make the plot
ggplot(Species_Data, 
       aes(x=as.factor(id), 
           y=value,
           fill=group)
       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 80, xend = start, yend = 80),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 60, xend = start, yend = 60),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 40, xend = start, yend = 40),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 20, xend = start, yend = 20),  colour = Ticks_Color, alpha=1, size=0.3 , inherit.aes = FALSE ) +
  # Add median lines for each gropup
  geom_segment(data=median_data, aes(x = end, y = median, xend = start+5, yend = median, colour = group),
               alpha=1, size=0.5 , inherit.aes = FALSE ) +
  # Add text showing the value of each line
  annotate("text", 
           x = rep(max(Species_Data$id),5),
           y = Seq_axis_spp,
           label = c(Seq_axis_spp[-5],">100"),
           color=Ticks_Color, 
           size=3 , 
           angle=0, 
           fontface="bold",
           hjust=1) +
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  geom_text(data=label_data_rest,
            aes(x=id, y=101,
                label=individual,
                hjust=hjust), 
            color="black",
            fontface="italic",
            alpha=1,
            size=2.5,
            angle= label_data_rest$angle,
            inherit.aes = FALSE) +
  # Bold top 3 
  geom_text(data=Top_label_data,
            aes(x=id, y=101,
                label=individual,
                hjust=hjust), 
            color="black",
            fontface="bold.italic",
            alpha=1,
            size=2.5,
            angle= Top_label_data$angle,
            inherit.aes = FALSE) +
  # Add base line information
  geom_segment(data=base_data, 
               aes(x = start, 
                   y = -5, 
                   xend = end, 
                   yend = -5
                   ), 
               colour = "black",
               alpha=0.8, 
               size=0.6 , 
               inherit.aes = FALSE) +
  ylim(-100,110) + # sets the circle the first value the central the last value how wide
  theme_minimal() +
  theme(
    legend.position = c(0.5,0.5),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() + 
  scale_fill_manual("Ecosystem Preference",
                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
                               wes_palette(n = 4, name = "GrandBudapest2")
                    ),
                    na.value = "white"
  ) +
  scale_colour_manual("Ecosystem Preference",
                      values = c(wes_palette(n = 4, name = "GrandBudapest1"),
                                 wes_palette(n = 4, name = "GrandBudapest2")
                      ),
                      na.value = "white"
  )
# 
ggsave(
    plot = last_plot(),
    width = 12,
    height = 12,
    units = "in",
    filename = "Species_circular_over20.png",
    path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
  )

@@

>>>>

### Function `Mclapply_Hack`

This function will hack the `mclappy()` function to work in PC and use multiple cores for the analysis. It was created by someone else and the original version is here: 
https://www.r-bloggers.com/implementing-mclapply-on-windows-a-primer-on-embarrassingly-parallel-computation-on-multicore-systems-with-r/

@@

# The hack

@@

### **Principal Routine**

```{r Trans_Spp_Control_Pannel, eval = T, echo = F}

@@

# Determine forlder for saving results
Results_Path <- paste(Data_Path,"Results/",Jurisdiction,"/",sep = "")

@@

# Just a warning for me not to forget
print(paste("You are running the model for",nrow(Exploited_Species),"Species at the",Jurisdiction,"level and will be saved at",Results_Path))
```

```{r Trans_Spp_Routine, eval = F, echo = F}

@@

## Functions needed

### Function `GetTransResults`

This function simply reads in the files and import them all as on large d.f

@@

### Function `CleanResults`

There are quite a few inconsistencies between the names of territories within the SAU shapefile, the distribution data and the UN database. The following function cleans up the names, some of them manually some of the automatic. It also removes the "transboundary nature" of those species shared by two territories that belong to the same nation (e.g. Brazil mainland and Brazil (Fernando de Noronha) or US Gulf of Mexico and US East coast). Finally, there is an annoying thing coding issue between MAC and Windows related to characters so I have to also fix for that, manually.

```{r funCleanResults, eval = T, echo = F}

@@

# Clean out countries that share with their own borders (e.g. Brazil mainland and Brazil (Fernando de Noronha))
  Auto_Remove_Territories <- Data %>%   
    rename(FishingRegion=Territory) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(TaxonKey,
           Territory= FishingRegion,
           FishingRegion=Neighbour, 
           Model_Index,
           Area_Index,
           CT_fishing_entity= fishing_entity) %>% 
    left_join(Clean_sau_eez_fes,
              by = "FishingRegion") %>% 
    select(1,2, 
           Neighbour = FishingRegion,
           Model_Index:CT_fishing_entity,
           NT_fishing_entity= fishing_entity,
           everything()) %>% 
    mutate(
      CT_fishing_entity = ifelse(is.na(CT_fishing_entity),paste(Territory),paste(CT_fishing_entity)),
      NT_fishing_entity = ifelse(is.na(NT_fishing_entity),paste(Neighbour),paste(NT_fishing_entity)),
      Same_Nation = ifelse(CT_fishing_entity==NT_fishing_entity,"Yes","No")
    )

@@

  # List of territories to eliminate (No other neighobors but mainland)
  Islands_to_Remove <- c(
    "Brazil (Fernando de Noronha)",
    "Brazil (St Paul and St. Peter Archipelago)",
    "Hawaii Main Islands (USA)",
    "Hawaii Northwest Islands (USA)",
    "Juan Fernandez Islands (Chile)",
    "Kermadec Isl. (New Zealand)"
  )

  # Complete list of territories to remove from dataset (Including islands)
  Territories_to_Remove <- Data %>% 
    filter(
      Territory %in% Islands_to_Remove |
        Neighbour %in% Islands_to_Remove |
        Territory == "Balearic Island (Spain)" & Neighbour == "Spain (Mediterranean and Gulf of Cadiz)" |
        Territory == "British Virgin Isl. (UK)" & Neighbour == "Anguilla" |
        Neighbour == "British Virgin Isl. (UK)" & Territory == "Anguilla" |
        Territory == "Corsica (France)" & Neighbour == "France (Mediterranean)" |
        Neighbour == "Corsica (France)" & Territory == "France (Mediterranean)" |
        Territory == "Crete (Greece)" & Neighbour == "Grece" |
        Neighbour == "Crete (Greece)" & Territory == "Grece" |
        Territory == "Cyprus (North)" & Neighbour == "Cyprus (South)" |
        Neighbour == "Cyprus (North)" & Territory == "Cyprus (South)" |
        Territory == "Channel Isl. (UK)" & Neighbour == "United Kingdom" |
        Neighbour == "Channel Isl. (UK)" & Territory == "United Kingdom" |
        Territory == "Glorieuse Islands (France)" & Neighbour == "Mayotte (France)" |
        Neighbour == "Glorieuse Islands (France)" & Territory == "Mayotte (France)" |
        Territory == "Guam (USA)" & Neighbour == "Northern Marianas (USA)" |
        Neighbour == "Guam (USA)" & Territory == "Northern Marianas (USA)" |
        Territory == "Italy" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Italy" & Territory == "Sardinia (Italy)" |
        Territory == "Italy" & Neighbour == "Sicily (Italy)" |
        Neighbour == "Italy" & Territory == "Sicily (Italy)" |
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (main islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (main islands)"|
        Territory == "Japan (Daito Islands)" & Neighbour == "Japan (Ogasawara Islands)"|
        Neighbour == "Japan (Daito Islands)" & Territory == "Japan (Ogasawara Islands)"|
        Territory == "Norway" & Neighbour == "Svalbard Isl. (Norway)" |
        Neighbour == "Norway" & Territory == "Svalbard Isl. (Norway)" |
        Territory == "Sicily (Italy)" & Neighbour == "Sardinia (Italy)" |
        Neighbour == "Sicily (Italy)" & Territory == "Sardinia (Italy)" |
        Territory == "South Africa (Atlantic Coast)" & Neighbour == "South Africa (Indian Ocean Coast)" |
        Neighbour == "South Africa (Atlantic Coast)" & Territory == "South Africa (Indian Ocean Coast)" |
        Territory == "USA (Alaska, Arctic)" & Neighbour == "USA (Alaska, Subarctic)" |
        Neighbour == "USA (Alaska, Arctic)" & Territory == "USA (Alaska, Subarctic)"
    ) %>%
    group_by(Territory,Neighbour) %>% 
    summarise(n())

  # Cleaned results 
  Clean_Results <- Auto_Remove_Territories %>% 
    anti_join(Territories_to_Remove,
              by = c("Territory","Neighbour")
    ) %>% 
    filter(Same_Nation == "No") %>% 
    select(-8,-9) %>% 
    # Fix coding issues between MAC and Windows
    mutate(
    Territory = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Territory),
    Territory = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Territory),
    Territory = gsub("R<e9>union (France)","Réunion",Territory),
    Neighbour = gsub("Cura<e7>ao (Netherlands)","Curaçao (Netherlands)",Neighbour),
    Neighbour = gsub("C<f4>te d'Ivoire","Côte d'Ivoire",Neighbour),
    Neighbour = gsub(" R<e9>union (France)","Réunion",Neighbour)
    )

@@

In here we load and cleaned the multiple external datasets requred to produce the manuscript figures

@@

# Updates result's path for the jurisdiction
Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")

@@

# Load Land shapefile
path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")

# The File
fnam_world_land <- "ne_50m_admin_0_countries.shp"

# Load it!
World_land_sf <- st_read(dsn = path_world_land,
                         layer =file_path_sans_ext(fnam_world_land)) %>% 
  rename(Territory = NAME)

@@

# Load SAU shapefile name and paths

# Load it!
World_sf <- st_read(dsn = path_world,
                    layer =file_path_sans_ext(fnam_world)) %>% 
  rename(Territory = Name)

@@

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(Data_Path,"Distribution_Data/Species_Status.csv", sep ="")) %>% 
  rename(TaxonKey = Species)

@@

# Load and clean transboundary results
Results_Trans <- GetTransResults(Spp)

@@

@@

Determine transboundary stocks and countries based on selected trsholds. We created two tresholds (levels of uncertanty), in here we can chose which level we wanna work with.

```{r Results_Tresholds, eval = F, echo = F}

@@

Determine the number of species per territory

```{r Data_per_Territory, eval = F, echo = F}

@@

# Get Catch data for mapping (Currently not used)

# Catch_Country <- Sau_Catch_Data %>% 
#   group_by(FishingRegion=Territory) %>% 
#   summarise(Total_Catch = round(sum(Mean_Catch,na.rm=T),2)) %>% 
#   filter(!(is.na(FishingRegion))) %>% 
#   left_join(Clean_sau_eez_fes) %>% 
#   group_by(Territory = fishing_entity) %>% 
#   summarise(Total_Catch = sum(Total_Catch,na.rm=T)) %>% 
#   mutate(Territory = gsub("USA","United States of America",Territory))

@@

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, Territory = fishing_entity) %>% 
  summarise(n=n()) %>% 
  select(-n) %>% 
  left_join(Tresholded_T_Data_x) %>% 
  left_join(Sau_Revenue_Data) %>% 
  group_by(Territory) %>% 
  summarise(Total_USD = (sum(Mean_Value,na.rm=T))/1000000) %>% # Million of USD
  mutate(Territory = ifelse(Territory == "USA","United States of America",Territory),
         Bins = cut(Total_USD,breaks = 4),
         Bins_Plot = cut(Total_USD,breaks = 4,
                         labels = c('super low', 'low','high','super high'))
  ) %>% 
  filter(Total_USD > 0)
```

@@

Produce the map of transboundary species within each EEZ and the value in catch/revenue within each country

@@

@@

```{r Circular_Country_Data, eval = T, echo = F}

@@

Create figures that are based in species (e.g. number of countries each species has)

```{r Circular_Spp_Data, eval = T, echo =F}

@@

# Use rfishbase to get species environment
Species_list <- Species_Trans %>% 
  mutate(scientific_name = paste(Genus,Species)) %>% 
  pull(scientific_name)

Species_environ_list <- rbind(species(Species_list, #species from rfishbase package
                                      fields = species_fields$habitat[4])
) %>% 
  mutate(scientific_name = Species_list)

Species_Data <- Tresholded_T_Data %>% 
  group_by(TaxonKey) %>% 
  summarise(n_trans_spp = length(unique(Territory))) %>% 
  left_join(Exploited_Species) %>%
  rename(scientific_name = TaxonName) %>% 
  left_join(Species_environ_list) %>%
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"Other",paste(DemersPelag)),
         n_trans_spp = ifelse(n_trans_spp > 100, 100, n_trans_spp)) %>% 
  select(individual=scientific_name,
         value = n_trans_spp,
         group = DemersPelag) %>% 
  arrange(group,value) %>% 
  filter(value > 20)  # remove all species under 20 (way too many to plot!)

@@

# Set a number of 'empty bar' to add at the end of each group
Char <- as.factor(Species_Data$group)
empty_bar <- 2
to_add <- data.frame( matrix(NA, empty_bar*nlevels(Char), ncol(Species_Data)) )
colnames(to_add) <- colnames(Species_Data)
to_add$group <- rep(levels(Char), each=empty_bar)
Species_Data <- rbind(Species_Data, to_add)
Species_Data <- Species_Data %>% arrange(group,value)
Species_Data$id <- seq(1, nrow(Species_Data))

@@

### ------------------- ###
# Make the plot
### ------------------- ###
ggplot(Species_Data, 
       aes(x=as.factor(id), 
           y=value,
           fill=group)
       ) +       # Note that id is a factor. If x is numeric, there is some space between the first bar
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, 
               aes(x = end, y = 100, xend = start, yend = 100), 
               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  geom_segment(data=grid_data,
               aes(x = end, y = 80, xend = start, yend = 80),  
               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  geom_segment(data=grid_data, 
               aes(x = end, y = 60, xend = start, yend = 60),  
               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  geom_segment(data=grid_data, 
               aes(x = end, y = 40, xend = start, yend = 40),  
               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  geom_segment(data=grid_data, 
               aes(x = end, y = 20, xend = start, yend = 20), 
               colour = Ticks_Color, alpha=1, size=0.3, inherit.aes = FALSE) +
  # Add median lines for each gropup
  geom_segment(data=median_data, 
               aes(x = end, y = median, xend = start+5, yend = median, colour = group),
               alpha=1, size=0.5 , inherit.aes = FALSE) +
  # Add text showing the value of each line
  annotate("text", 
           x = rep(max(Species_Data$id),5),
           y = Seq_axis_spp,
           label = c(Seq_axis_spp[-5],">100"),
           color=Ticks_Color, 
           size=3, 
           angle=0, 
           fontface="bold",
           hjust=1) +
  geom_bar(aes(x=as.factor(id),
               y=value,
               fill=group),
           stat="identity",
           alpha=0.5) +
  geom_text(data=label_data_rest,
            aes(x=id, y=101,
                label=individual,
                hjust=hjust), 
            color="black",
            fontface="italic",
            alpha=1,
            size=2.5,
            angle= label_data_rest$angle,
            inherit.aes = FALSE) +
  # Bold top 3 
  geom_text(data=Top_label_data,
            aes(x=id, y=101,
                label=individual,
                hjust=hjust), 
            color="black",
            fontface="bold.italic",
            alpha=1,
            size=2.5,
            angle= Top_label_data$angle,
            inherit.aes = FALSE) +
  # Add base line information
  geom_segment(data=base_data, 
               aes(x = start, 
                   y = -5, 
                   xend = end, 
                   yend = -5
               ), 
               colour = "black",
               alpha=0.8, 
               size=0.6 , 
               inherit.aes = FALSE) +
  ylim(-100,110) + # sets the circle the first value the central the last value how wide
  theme_minimal() +
  theme(
    legend.position = c(0.5,0.5),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm") 
  ) +
  coord_polar() + 
  scale_fill_manual("Ecosystem Preference",
                    values = c(wes_palette(n = 4, name = "GrandBudapest1"),
                               wes_palette(n = 4, name = "GrandBudapest2")
                    ),
                    na.value = "white"
  ) +
  scale_colour_manual("Ecosystem Preference",
                      values = c(wes_palette(n = 4, name = "GrandBudapest1"),
                                 wes_palette(n = 4, name = "GrandBudapest2")
                      ),
                      na.value = "white"
  )

ggsave(
  plot = last_plot(),
  width = 12,
  height = 12,
  units = "in",
  filename = "Species_circular_over20.png",
  path = "/Volumes/DATA/JULIANO_NEYMAR/FishForVisa/Figures/"
)

@@

```{r round_map, eval = F, echo = F}
# #### Round map tryout

# ### EEZ shapefile
# eez  = readRDS(paste(Data_Path,"Spatial_Data/eez_simplified.rds",sep="")) #taken from cotterel https://github.com/cottrellr/shocks
# 
# eez = spTransform(eez, CRS("+proj=longlat"))
# eez = spTransform(eez, CRS("+proj=wintri"))
# eez = fortify(eez) 
# 
# World_sf_si <- World_sf %>%
#   st_transform(crs = 4326
#
